Active Transfer Learning

### 2018-02-28 paper/paper.tex
Added least-squares to the write-up

\usepackage[utf8]{inputenc} % allow utf-8 input
\usepackage[T1]{fontenc}    % use 8-bit T1 fonts
\usepackage{hyperref}       % hyperlinks
\usepackage{url}            % simple URL typesetting
\usepackage{booktabs}       % professional-quality tables
\usepackage{amsfonts}       % blackboard math symbols
\usepackage{nicefrac}       % compact symbols for 1/2, etc.
\usepackage{microtype}      % microtypography
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}

@@

>>>>

\usepackage[utf8]{inputenc} % allow utf-8 input
\usepackage[T1]{fontenc}    % use 8-bit T1 fonts
\usepackage{hyperref}       % hyperlinks
\usepackage{url}            % simple URL typesetting
\usepackage{booktabs}       % professional-quality tables
\usepackage{amsfonts}       % blackboard math symbols
\usepackage{nicefrac}       % compact symbols for 1/2, etc.
\usepackage{microtype}      % microtypography
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{bm}
\usepackage{todonotes}

@@

\subsection{Regularized Bellman Residual Minimization with Gaussian Priors}

Consider solving the target task given a dataset $D$ of $N$ samples. The posterior distribution over optimal $Q$-functions is:
\begin{equation}
P(Q^* \mid D) \propto P(D \mid Q^*)P(Q^*)
\end{equation}
Bounding the likelihood $P(D \mid Q^*)$ ({\color{red}FIND A BETTER DERIVATION}) and taking the maximum of the log-posterior, we obtain the following optimization problem:
\begin{equation}
\min_{Q\in\mathcal{Q}} ||B(Q)||_{p,D}^p - \log P(Q) 
\end{equation}
Then, let us specify a particular hypothesis space $\mathcal{Q}$. We consider $Q$-functions $Q_{\bm{w}}$ parameterized by the vector $\bm{w}$. Our optimization problem becomes:
\begin{equation}
\min_{\bm{w}} ||B(\bm{w})||_{p,D}^p - \log P(\bm{w}) 
\end{equation}
We model the prior distribution over the optimal parameters $\bm{w}$ as a Gaussian. That is, we assume:
\begin{equation}
P(\bm{w}) = \mathcal{N}(\bm{\mu},\bm{\Sigma})
\end{equation}
Then, our optimization, adopting the $l_2$-norm, becomes:
\begin{equation} \label{eq:optim}
\min_{\bm{w}} ||B(\bm{w})||_{D}^2 + ||\bm{w}-\bm{\mu}||_{\bm{\Sigma}} = \min_{\bm{w}} \frac{1}{N}\sum_{i=1}^N\left\lvert y_i - Q_{\bm{w}}(s_i,a_i) \right\rvert^2 + ||\bm{w}-\bm{\mu}||_{\bm{\Sigma}}
\end{equation}
where $y_i = r_i + \gamma\max_{a'}Q_{\bm{w}}(s_i',a')$ and $||\bm{x}||_{\bm{A}} \triangleq \bm{x}^T\bm{A}^{-1}\bm{x}$ for $\bm{A}$ positive definite matrix.

\paragraph{Linear model}

We assume a linear model for the $Q$-functions: $Q_{\bm{w}}(s,a) = \bm{w}^T\bm{\phi}(s,a)$. Here $\bm{\phi}$ is a $K$-dimensional feature vector. Then, the solution to the optimization problem of Eq. \eqref{eq:optim} can be computed in closed form as follows:
\begin{equation}
\bm{w}^* = \left( \bm{A}^T\bm{A} + \bm{\Sigma}^{-1} \right)^{-1} \left( \bm{A}^T\bm{b} + \bm{\Sigma}^{-1}\bm{\mu} \right) 
\end{equation}
where $\bm{A}$ is an $N\times K$ matrix containing the feature vectors at each data point $(s_i,a_i)$ and $\bm{b}$ is an $N$-dimensional vector containing their targets $y_i$.
